Earth_microbiome_MS

### 2019-08-09 Earth_microbiome_MS copy.Rmd
updated

#Create table dispaying the average prevalence of each phyla per sample and the total reads for all phyla in the data frame
plyr::ddply(prevdf, "Phylum (unfiltered)", function(df1){cbind(mean(df1$Prevalence),sum(df1$Prevalence))})

>>>>

#Create table dispaying the average prevalence of each phyla per sample and the total reads for all phyla in the data frame
plyr::ddply(prevdf, "Phylum", function(df1){cbind(mean(df1$Prevalence),sum(df1$Prevalence))})
